TBD

### 2021-02-18 outputs/paper/paper.Rmd
Q5, Q6, Q13 figures/tables added

all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
control_group <-
  readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  filter(type == "Control")
treatment_group <-
  readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  filter(type == "Treated")
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q2)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Scale of Restaurant",
       y = "# of Restaurants",
       title = "Q2") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q3)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Fine Dining", "Casual Dining", "Fast-food/quick service", "Other")) +
  labs(x = "Type of Restaurant",
       y = "# of Restaurants",
       title = "Q3") +
  theme_minimal()

ggplot(data = all_simulated_dataset, mapping = aes (x = Q4)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("1-4 years", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       title = "Q4") +
  theme_minimal()

```{r Q5, echo = FALSE, message = FALSE}
### How many people do you currently employ?
### Prior to (intervention start date), how many people did you employ?
### Control

### line graph

```{r Q6, echo = FALSE, message = FALSE}
### How many people do you currently employ?
### Prior to (intervention start date), how many people did you employ?
### Treated

### line graph

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did revenue increase, decrease, or remain the same compared to last month?",
       y = "# of restaurants",
       title = "Q7",
       fill = "Type") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_minimal()

### make this a line graph

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "15% or less", "15-30%","30-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()

### make this a line graph instead
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = "Q10",
       fill = "Legend") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "Other", "In-house delivery service", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Q11",
       fill = "Legend") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Was there a reduction in restaurant hours?",
       y = "# of restaurants",
       title = "Q12",
       fill = "Legend") +
  theme_minimal()

@@

### line graph

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did you reduce the # of days you were open to the public between (start date) and (end date)?",
       y = "Y",
       title = "Q14",
       fill = "Legend") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "How many days per week did you reduce by?",
       y = "# of restaurants",
       title = "Q15",
       fill = "Legend") +
  theme_minimal()

>>>>

all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
#control_group <-
 # readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  #filter(type == "Control")
#treatment_group <-
 # readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  #filter(type == "Treated")
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q2)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Scale of Restaurant",
       y = "# of Restaurants",
       title = "Q2") +
  theme_minimal()
```

ggplot(data = all_simulated_dataset, mapping = aes (x = Q3)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Fine Dining", "Casual Dining", "Fast-food/quick service", "Other")) +
  labs(x = "Type of Restaurant",
       y = "# of Restaurants",
       title = "Q3") +
  theme_minimal()
```

ggplot(data = all_simulated_dataset, mapping = aes (x = Q4)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("1-4 years", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       title = "Q4") +
  theme_minimal()
```

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?

t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))

t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)

total <- merge(t1, t2, by = c("type"))

kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))

@@

```{r Q5 + Q6 Bar Graphs, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?

#ggplot(data = treatment_group, mapping = aes(x = Q5)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "# of employees prior to (date) for treatment group") +
  #theme_minimal()

#ggplot(data = control_group, mapping = aes(x = Q5)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "# of employees prior to (date) for control group",
     #   group = "Legend") +
  #theme_minimal()

#ggplot(data = treatment_group, mapping = aes(x = Q6)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "Current # of employees for treatment group") +
  #theme_minimal()

#ggplot(data = control_group, mapping = aes(x = Q6)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "Current # of employees for control gruop") +
  # theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did revenue increase, decrease, or remain the same compared to last month?",
       y = "# of restaurants",
       title = "Q7",
       fill = "Type") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "15% or less", "15-30%","30-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = "Q10",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "Other", "In-house delivery service", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Q11",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Was there a reduction in restaurant hours?",
       y = "# of restaurants",
       title = "Q12",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = "Q13",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did you reduce the # of days you were open to the public between (start date) and (end date)?",
       y = "Y",
       title = "Q14",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "How many days per week did you reduce by?",
       y = "# of restaurants",
       title = "Q15",
       fill = "Legend") +
  theme_minimal()
```
